Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-11 analysis/paper_draft3.Rmd
minor edit to last line in conclusion

In future work we hope to examine data-driven approached to the selection of $\alpha$; where the degree of incompatibility can be estimated and used to inform the choice of the degree of discounting to apply to historical data. Knowing how to quantify incompatibility and how to specify and appropriate prior for  $\alpha$ is an area of active research [e.g., @Pawel2022]

>>>>

In future work we hope to examine data-driven approach to selecting $\alpha$; where the degree of incompatibility can be estimated and used to inform the choice of the degree of discounting to apply to historical data. Knowing how to quantify incompatibility and how to specify an appropriate prior for $\alpha$ is an area of active research [e.g., @Pawel2022]
